Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-06 Manuscript/manuscript.Rmd
updated manuscript

The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins [??? across all chromosomes? If I do 44948*5000, I get 224740000, which is 1 billion bases less than the size of the genome. What is going on?; !!!This is only CHR1 for right now] (Table 2). There were only 3083 (6.9%) bins that overlapped with a flanked TAD boundary [??? What is flanked TAD boundary? Why do we care?]. An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slighly less degree of class imbalance. The percentage of imbalance for each of the other resolutions were found to be  14.0%, 13.7%, and 12.2% for 25 kb, 50kb, and 100kb resolutions respectively. [??? Add exact numbers of class imbalance for each resolution; !!! added exact numbers] (Supplementaty Table 8). The overall average perentage of class imbalance across all data resolutions was 13.2% [??? Do not understand. I understand the ratio of #minority/#majority, but what % tells?].  After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4). That is, the ratio of bins that overlapped with flanked TAD boundaries to bins that did not was 1:1.

>>>>

The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins [??? across all chromosomes? If I do 44948*5000, I get 224740000, which is 1 billion bases less than the size of the genome. What is going on?; !!!This is only CHR1 for right now] (Table 2). There were only 3083 (6.9%) bins that overlapped with a flanked TAD boundary [??? What is flanked TAD boundary? Why do we care?]. An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slighly less degree of class imbalance. The percentage of imbalance for each of the other resolutions were found to be  14.0%, 13.7%, and 12.2% for 25 kb, 50kb, and 100kb resolutions respectively. [??? Add exact numbers of class imbalance for each resolution; !!! added exact numbers] (Supplementaty Table 2). [??? Do not understand. I understand the ratio of #minority/#majority, but what % tells?; !!!was overally average of class imbalance for the 4 data resolutions; removed sentence; doesn't seem relevant].  After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4). That is, the ratio of bins that overlapped with flanked TAD boundaries to bins that did not was 1:1.
